Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-09-06 doc/RMD/mlg-mcg.Rmd
update figure 1

```{r barplots, fig.width = 10, fig.height = 5}
mcg_graph <- mcgs %>% 
  filter(Samples > 1) %>%
  gather(type, count, MLGs, Samples, -Evenness) %>%
  arrange(desc(type), desc(count)) %>%
  rename(Type = type) %>%
  mutate(Type = ifelse(Type == "MLGs", "MLHs", Type)) %>%
  mutate(MCG = forcats::fct_inorder(MCG, ordered = TRUE)) %>%
  ggplot(aes(x = MCG, y = count, group = Type, fill = Type, alpha = Evenness)) +
  geom_col(aes(width = ifelse(Type == "MLHs", 0.5, 0.85)), color = "black", position = "identity") +
  annotate(geom = "rect", xmin = 0.5, xmax = 8.5, ymin = 0, ymax = 75, color = "black", size = 1.5, alpha = 0, lty = 2) +
  # annotate(geom = "text", x = 18, y =35, 
  #          label = sprintf("Mean Evenness: %.3f", mean(mcgs$Evenness, na.rm = TRUE))) +
  scale_fill_manual(values = c("black", "white")) +
  scale_y_continuous(expand = c(0, 2)) +
  # scale_alpha(breaks = c(0.5, 0.75, 1)) +
  theme_minimal(base_size = 16, base_family = "Helvetica") +
  # coord_flip() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.grid.major.y = element_line(color = "grey50")) +
  theme(panel.grid.minor.y = element_line(color = "grey70")) +
  theme(legend.box.just = "top") +
  theme(legend.box.margin = unit(c(0, 6.55, 0, 0), "lines")) +
  theme(legend.box.background = element_rect(fill = "white", color = "black")) +
  theme(legend.box = "horizontal") +
  theme(legend.position = c(0.77, 0.75)) +
  theme(aspect.ratio = 1/2) +
  labs(list(
    alpha = "MLH\nEvenness"
  ))

@@

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% (mcgs %>% arrange(desc(Samples)) %>% slice(1:8) %>% pull(MCG)))
top5g <- make_mcgmlg_graph(top5)
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
# set.seed(2017-05-08)
set.seed(2017-08-1)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "fr", weights = rep(1, length(E(top5g))))
top5lay$community <- inner_join(data_frame(vertex = top5lay$name), the_communities)$comm
levels(top5lay$type) <- c("Multilocus Haplotype", "Mycelial Compatibility\nGroup")
t5g <- ggraph(top5lay) +
  geom_node_circle(aes(r = size, fill = type)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), 
                     color = type, 
                     size = size/10),
                 show.legend = FALSE) +
  coord_fixed() +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_fill_manual(values = c("black", "white")) +
  scale_color_manual(values = c("white", "black")) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  # theme(legend.position = c(0.85, 0.35), legend.direction = "vertical") +
  theme(legend.position = c(0.5, 0), legend.direction = "horizontal", legend.box = "horizontal") +
  theme(legend.box.spacing = unit(-1, "lines")) +
  theme(legend.spacing.x = unit(0, "lines")) +
  # theme(legend.box.background = element_rect(color = "black")) +
  theme(legend.text = element_text(size = 10)) +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines"))
t5g$labels$edge_width <- "shared isolates"
t5g$labels$fill <- ""
t5g

>>>>

```{r barplots, fig.width = 10, fig.height = 5}
mcg_graph <- mcgs %>% 
  filter(Samples > 1) %>%
  gather(type, count, MLGs, Samples, -Evenness) %>%
  arrange(desc(type), desc(count)) %>%
  rename(Type = type) %>%
  mutate(Type = ifelse(Type == "MLGs", "MLHs", Type)) %>%
  mutate(MCG = forcats::fct_inorder(MCG, ordered = TRUE)) %>%
  ggplot(aes(x = MCG, y = count, group = Type, fill = Type, alpha = Evenness)) +
  geom_col(aes(width = ifelse(Type == "MLHs", 0.5, 0.85)), color = "black", position = "identity") +
  annotate(geom = "rect", xmin = 0.5, xmax = 8.5, ymin = 0, ymax = 75, color = "black", size = 1.125, alpha = 0, lty = 2) +
  # annotate(geom = "text", x = 18, y =35, 
  #          label = sprintf("Mean Evenness: %.3f", mean(mcgs$Evenness, na.rm = TRUE))) +
  scale_fill_manual(values = c("black", "white"), labels = c("MLHs", "Isolates")) +
  scale_y_continuous(expand = c(0, 2)) +
  # scale_alpha(breaks = c(0.5, 0.75, 1)) +
  theme_minimal(base_size = 16, base_family = "Helvetica") +
  # coord_flip() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.grid.major.y = element_line(color = "grey50")) +
  theme(panel.grid.minor.y = element_line(color = "grey70")) +
  theme(legend.box.just = "top") +
  theme(legend.box.margin = unit(c(0, 6.55, 0, 0), "lines")) +
  theme(legend.box.background = element_rect(fill = "white", color = "black")) +
  theme(legend.box = "horizontal") +
  theme(legend.position = c(0.77, 0.75)) +
  theme(aspect.ratio = 1/2) +
  labs(list(
    alpha = "MLH\nEvenness"
  ))

@@

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% (mcgs %>% arrange(desc(Samples)) %>% slice(1:8) %>% pull(MCG)))
top5g <- make_mcgmlg_graph(top5)
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
# set.seed(2017-05-08)
set.seed(2017-08-1)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "fr", weights = rep(1, length(E(top5g))))
top5lay$community <- inner_join(data_frame(vertex = top5lay$name), the_communities)$comm
levels(top5lay$type) <- c("Multilocus Haplotype", "Mycelial Compatibility\nGroup")
t5g <- ggraph(top5lay) +
  geom_node_circle(aes(r = size, fill = type)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), # ifelse(size > 0.1, gsub("MLG.", "", name), ""), 
                     color = type, 
                     size = size/10),
                 show.legend = FALSE) +
  coord_fixed() +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_fill_manual(values = c("black", "white")) +
  scale_color_manual(values = c("white", "black")) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  # theme(legend.position = c(0.85, 0.35), legend.direction = "vertical") +
  theme(legend.position = c(0.5, 0), legend.direction = "horizontal", legend.box = "horizontal") +
  theme(legend.box.spacing = unit(-1, "lines")) +
  theme(legend.spacing.x = unit(0, "lines")) +
  # theme(legend.box.background = element_rect(color = "black")) +
  theme(legend.text = element_text(size = 10)) +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines"))
t5g$labels$edge_width <- "Shared Isolates"
t5g$labels$fill <- ""
t5g
